Untitled

### 2022-12-21 Figuring_Q3.Rmd
Adding in code for part d and e of Q3 (MCMC question)

>>>>

# Calculating density using proposal density for each row (p_{x})
proposal.density.cur <- proposal.density.new <- NULL
for (i in 1:length(initStateProbs)){
proposal.density.new[i] <- calcDirichletPDF(proposal[i,],20*PT[i,,j-1])
proposal.density.cur[i] <- calcDirichletPDF(PT[i,,j-1],20*PT[i,,j-1])
}
#Finding probability of P_T using joint probability 
proposal.density.cur <- exp(sum(proposal.density.cur))
proposal.density.new <- exp(sum(proposal.density.new))
